Verifying Demonstrations

### 2018-10-29 paper/ZKPK.tex

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma]
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
Greek letters are known only to the prover and use for the information for which the prover wishes to prove knowledge, all other letters are known by the verifier.

>>>>

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma],
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, all other letters are known by the verifier.

### 2018-10-29 paper/protocol.tex
Changes font size for figures to \small

\begin{figure}
  \centering
  %\footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and the protester's \(\pid\).
    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
    The protester constructs \(\prf_P\) analogously.
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  %\footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participation: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The protester sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the protester and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the protester as the prover and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k_P+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows.
(Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple 
times to achieve security.)
The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the protester computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the protester.
As a consequence, both the protester and the witness have the tuple \(\pi = 
  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
protester (\cref{fig:ProofFig}).

>>>>

\begin{figure}
  \centering
  \small
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and the protester's \(\pid\).
    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
    The protester constructs \(\prf_P\) analogously.
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid] \quad \land \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid] \quad \land \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid] \quad \land \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participation: \(\psh\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The protester sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the protester and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the protester as the prover and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r', \cid, r_\cid) : \right. \\
    v^{r'} = v_x v_{xy}^{k_P} v_{xy}^{\prime r} \land \pid = g_T^{1/(k_P+\cid)} 
    \land \\
    \left. c = g^\cid Z^{r_\cid}
  \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows.
(Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple 
times to achieve security.)
The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the protester computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
  = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the protester.
As a consequence, both the protester and the witness have the tuple \(\psh = 
  (\pid, \wid, t_s, t_s', l)\), which forms a proof share for the protester 
(\cref{fig:ProofFig}).
